\documentclass[11pt]{article}

\usepackage[ascii]{inputenc}
\usepackage[margin=0.5in, top=0.1cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multicol}


\graphicspath{{.}}

\begin{document}
 \thispagestyle{empty}
\begin{center}
\Large{\textbf{Erick Alejandro Carrillo Lopez} \\
  \textbf{Mail:} erickcarrillo1024@outlook.com\\
  \textbf{Tel:} (+52)3319911674}
\quad\quad \href{https://github.com/alecksandr26}{\color{blue}{Github}}
  \quad\quad \href{https://www.linkedin.com/in/erick-alejandro-carrillo-lopez-988112219/}{\color{blue}{Linkedin}}
\end{center}
\vspace{-0.5cm}
\section*{Education}
\vspace{-0.4cm}
\titlerule[0.3pt]
\vspace{-0.4cm}

\begin{multicols}{2}
  \noindent
  \textbf{B.S. Computer engineering}\\
  University of Guadalajara
  
  \columnbreak
  \noindent
  Began in \textbf{January - 2021}\\
  Expected Graduation \textbf{December -  2024}
\end{multicols}
\vspace{-0.3cm}
\begin{itemize}[noitemsep, nolistsep]
\item \textbf{GPA:} 90/100
\item \textbf{Notable Courses:} Data Structures, Algorithms, Database, Statistics and Numerical Analysis,
  Compiler and Traslation, Theory of Computation, Computer networks, Computer Architecture
\end{itemize}
\vspace{-0.4cm}
\section*{Projects}
\vspace{-0.4cm}
\titlerule[0.3pt]
\vspace{0.1cm}
\subsection*{\href{https://github.com/alecksandr26/cnet}{\color{blue}{Complex Neural Networks Framework From Scratch}}:}
\vspace{-0.3cm}
\begin{itemize}[noitemsep, nolistsep]
\item Jul, 2023
\item Ongoing \textbf{CMake} project exploring the utilization of weighted complex numbers in real-valued
  \textbf{neural network models} for potential \textbf{cost-effectiveness and accuracy} improvements.
\item Developed with \textbf{optimized matrix operations} and activation functions for enhanced performance.
  Compared with numpy's array matrix multiplication and GNU Scientific Library,
  \textbf{the implementation is slightly faster}.
  My estimation, based on testing with a six-core processor, suggests an improvement ranging from
  approximately \textbf{37.841\% to 41.557\%}.
\item Implemented in pure \textbf{C/C++}, leveraging \textbf{OMP} for parallelize several for loops
  and \textbf{SIMD} instructions for processor optimization. Unit tested using the
  \textbf{Google testing framework}.
\end{itemize}
\vspace{-0.3cm}
\subsection*{\href{https://github.com/alecksandr26/unittest-c}{\color{blue}{Unit Testing Framework for C in Linux:}}}
\vspace{-0.3cm}
\begin{itemize}[noitemsep, nolistsep]
\item May, 2023
\item Pure \textbf{C} project designed to simplify and streamline testing of \textbf{C} projects on
  \textbf{Linux}, inspired by Python's unit testing library and Google Test.
\item Offers more than 20 methods for \textbf{assertions and non-fatal assertions}, streamlining the
  process of creating isolated test cases. Additionally, includes automatic recompilation of test files
  for improved efficiency.
\item Developed entirely in \textbf{C} with a \textbf{Makefile} for seamless build automation.
\end{itemize}
\vspace{-0.3cm}
\subsection*{\href{https://github.com/alecksandr26/recipe-app-web}{\color{blue}{Cooking Recipes Web App:}}}
\vspace{-0.3cm}
\begin{itemize}[noitemsep, nolistsep]
\item Feb, 2023
\item Ongoing project aiming to create a user-friendly platform for sharing cooking recipes.
\item Features robust user management, allowing users \textbf{to search, upload, and rate recipes}.
\item Implemented in \textbf{Python} using \textbf{Flask} framework and various \textbf{Flask} libraries.
  Utilizes \textbf{MariaDB} for the relational database,
  \textbf{Bootstrap} for frontend development, and \textbf{Python's} default unittesting library.
\end{itemize}

\vspace{-0.5cm}
\section*{Technical Skills}
\vspace{-0.3cm}
\titlerule[0.3pt]
\vspace{0.1cm}

\begin{itemize}[noitemsep, nolistsep]
\item \textbf{Back-End:} Python, C/C++, Java, Rust, Clisp, Flask and Django.
\item \textbf{Front-End:} JavaScript, HTML, CSS, BootStrap, ReactJs and Tkinter.
\item \textbf{DataBase:} MySql, MariaDB, PostgreSQL, SqlServer and FireBase.
\item \textbf{Developer Tools:} Git, Emacs, Linux environment, CMake and Makefile.
\item \textbf{Languages:} Spanish(Native), English(Basic).
\end{itemize}
\vspace{-0.5cm}

\section*{Extracurriculars}
\vspace{-0.3cm}
\titlerule[0.3pt]
\vspace{0.1cm}
\begin{itemize}[noitemsep, nolistsep]
\item \textbf{Clubs:} "Club de Algoritmia CUCEI" (Algorithms club).
\item \textbf{Awards or Honors:} Acknowledged for exceptional contributions as part of the \textbf{"Eureka"}
  team, representing the \textbf{University of Guadalajara CUCEI}, at the
  \textbf{18th National Programming Contest} in October 2023.
\end{itemize}

\end{document}
